Linear instability underlying synchronous waving of marine grass in flow

### 2014-08-29 Paper/grass.tex
Figure 4 and caption, and title

\begin{document}
\title{Waving and swaying}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{Mahesh Bandi\footnote{work performed while visiting Brown University}}
\affiliation{Okinawa Institute of Science and Technology, Okinawa, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

\begin{figure}[htb]
\includegraphics[]{K_vs_shear_width_noshear}
\caption{Critical Wavenumber for different grass height as function of shear layer thickness}
\label{K_vs_shear}
\end{figure}
\begin{figure*}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens28_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens30_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens34_imgsc}}

\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens38_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens40_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens42_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens46_imgsc}}

\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens34_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens36_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens38_imgsc}}

\caption{$Re(\sigma)$ as function of wavenumber and Reynolds number for a given grass number density along with contour of zero growth rate ($Re(\sigma)$=0). The figures in each 
row corresponds to a particular grass height $\hg/H = 0.8$ for (a-d), 1.0 for (e-h) and  1.2 for (i-l), these figures are arranged in order of increasing grass 
number density. At low grass number density both the modes are indistinguishable, but as $N_g$ increases the distinction between the two modes become clear. For $N_g$ below
a critical value, the K-H mode sets the onset of flow instability whereas above the critical $N_{g}$ onset of flow instability is dominated by shear instability of flow above the grass}
\label{K_Re_sigma_set3}
\end{figure*}

>>>>

\begin{document}
\title{Linear instability underlying synchronous waving of marine grass in flow}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{Mahesh Bandi\footnote{work performed while visiting Brown University}}
\affiliation{Okinawa Institute of Science and Technology, Okinawa, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

@@

\begin{figure}[htb]
\includegraphics[]{K_vs_shear_width_noshear}
\caption{Critical Wavenumber for different grass height as function of shear layer thickness}
\label{K_vs_shear}
\end{figure}
\begin{figure*}

%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens31_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens32_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens34_imgsc}}
%\subfigure[]{\includegraphics[scale = 0.24]{Set3_dens38_imgsc}}

\begin{tabular}{cccc}
{\includegraphics[scale = 0.72]{Set4_dens28_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens30_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set4_dens34_imgsc}} \\
{\includegraphics[scale = 0.72]{Set5_dens38_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens40_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens42_imgsc}} &
{\includegraphics[scale = 0.72]{Set5_dens46_imgsc}} \\
{\includegraphics[scale = 0.72]{Set6_dens32_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens34_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens36_imgsc}} &
{\includegraphics[scale = 0.72]{Set6_dens38_imgsc}}
\end{tabular}

\caption{$Re(\sigma)$ as function of wavenumber and Reynolds number for a given grass number density along with the neutral curve ($Re(\sigma)$=0), for parameters shown in the corresponding panel.  
At low grass number density both the modes are indistinguishable, but as $N_g$ increases the unstable region splits into two labeled as ``Mode 1'' and ``Mode 2''. For $N_g$ below
a critical value, the Mode 1 sets the threshold $\Rey$ whereas above the critical $N_{g}$ onset is determined by Mode 2.}
\label{K_Re_sigma_set3}
\end{figure*}
